Chess collusion with hyper3 objects

### 2022-10-18 inst/collusion3.Rmd
minor rephrasing

We analyse results from Curacao 1962 using `hyper3` formalism using
the weighted Draw monster appraoch outlined in `kka.Rmd`:

@@

With this model, whatever the value of $D$ and $\lambda$, there is a
pathology which BT cannot deal with.  Still not quite 100% sure but it
seems that the maximum likelihood estimate of the players' strengths
is zero except for Fisher and Petrosian; and indeed we see Fisher at
57% and Petrosian at 42% [with $\lambda = 1.1, D=1.888$].  This on the
grounds that these players never lost playing black (there are some
$2\times 3$ tables at the end).  This might be considered a defect of
the probability model.

@@

```{r,label=loadjavelinandconvert}
cur_matches <- read.table("stockholm1962_matches.txt",header=FALSE)
head(cur_matches)
nrow(cur_matches)
```

@@

```{r,comparelikelihoods,cache=TRUE}
maxp(f(1.1,2.1),n=1,give=TRUE)
maxp(f(1.1,2.3),n=1,give=TRUE)
```

>>>>

We analyse results from Curacao 1962 using `hyper3` formalism using
the weighted Draw monster approach outlined in `kka.Rmd`:

@@

With this model [discussed in a broader context at `kka.Rmd`],
whatever the value of $D$ and $\lambda$, there is a pathology which BT
cannot deal with.  Still not quite 100% sure but it seems that the
maximum likelihood estimate of the players' strengths is zero except
for Fisher and Petrosian; and indeed we see Fisher at 57% and
Petrosian at 42% [with $\lambda = 1.1, D=1.888$].  This on the grounds
that these players never lost playing black (there are some $2\times
3$ tables at the end).  This might be considered a defect of the
probability model.

@@

```{r,label=loadjavelinandconvert}
cur_matches <- read.table("stockholm1962_matches.txt",header=FALSE)
colnames(cur_matches) <- c("white","black","result")
head(cur_matches)
nrow(cur_matches)
```

@@

```{r,comparelikelihoods,cache=TRUE}
m1121 <- maxp(f(1.1,2.1),n=1,give=TRUE)
m1123 <- maxp(f(1.1,2.3),n=1,give=TRUE)
```

```{r,showmaxpwithlam}
pie(m1121$par)
```
